Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex

@@

\begin{figure}
   \includegraphics[scale=.53]{query-times}
  \caption{Comparison of query times for various queries with different result set sizes (left to right: smaller to larger) between our three main types of indexes and sequential search (the only way to search strings that indexedDB offers). }
  \label{querytimes}
\end{figure}

@@

The data also shows that the number of results has an  impact on lookup time. The three graphs are tiered such that ``feel'', with the most results, is also the slowest query. While the lookup logic is parallelized so that the text for multiple matching document ids can be retrieved concurrently, the number of lookups that are done to retrieve this text has an impact on performance.

>>>>

\begin{figure}
   \includegraphics[scale=.2]{search-screenshot}
  \caption{Our local full-text search demo that we used to take the measurements described in this experiment.}
\end{figure}

@@

\begin{figure}
   \includegraphics[scale=.39]{query-times}
  \caption{Comparison of query times for various queries with different result set sizes (left to right: smaller to larger) between our three main types of indexes and sequential search (the only way to search strings that indexedDB offers). }
  \label{querytimes}
\end{figure}

@@

The data also shows that the number of results has an  impact on lookup time. The three graphs are tiered such that "feel", with the most results, is also the slowest query. While the lookup logic is parallelized so that the text for multiple matching document ids can be retrieved concurrently, the number of lookups that are done to retrieve this text has an impact on performance.

\subsection{Comparison}

As we have seen earlier in this section, prefix and suffix tries are very intensive to create in a key-value store, and thus, are better suited to smaller datasets. This is what initially motivated us to build the hybrid approach, which, as we have demonstrated, is orders of magnitude faster in index creation time and slightly faster in query time. However, the hybrid approach is less space efficient than tries (in the general case), since the entire path to the node needs to be stored as its key, which makes it better suited for shorter tokens. The inverted index is slightly (within the margin of error) slower for lookups than both tries, but this is likely due to the overhead of stemming.
